---
output: github_document
editor_options: 
  chunk_output_type: console
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# berraerkosar

<!-- badges: start -->
[![R-CMD-check](https://github.com/berkosarFIND/berraerkosar/workflows/R-CMD-check/badge.svg)](https://github.com/berkosarFIND/berraerkosar/actions)
<!-- badges: end -->

The goal of berraerkosar is to calculate the body mass index and to list the datasets that are present in different sheets of an excel file.

## Installation

You can install the development version of berraerkosar like so:

``` r
remotes::install_local(path = 'berraerkosar_0.0.0.9000.tar.gz')
```

## Example

This example shows how to calculate a body mass index using the bmi function.

```{r example}
library(berraerkosar)
## basic example code
```

This following examples show how to use the BMI function.

```{r bmi}
library(dplyr)
library(berraerkosar)

#Calculating a single BMI
bmi(mass = 80, height = 1.80) # Should give 24.7

#To insert BMI column on a data frame
data("data_weight")
data_weight %>%
  mutate(bmi = bmi(mass = mass, height = height))

```
