---
title: "flat_full.Rmd for working package"
output: html_document
editor_options: 
  chunk_output_type: console
---

<!-- Run this 'development' chunk -->
<!-- Store every call to library() that you need to explore your functions -->

```{r development, include=FALSE}
library(testthat)

bmi <- function(mass, height){
  bmi_calculated <- mass/(height * height)
  return(bmi_calculated)
}

```

<!--
 You need to run the 'description' chunk in the '0-dev_history.Rmd' file before continuing your code there.

If it is the first time you use {fusen}, after 'description', you can directly run the last chunk of the present file with inflate() inside.
--> 

# Include some data examples in your package

<!-- 
 Store your dataset in a directory named "inst/" at the root of your project.
 Use it for your tests in this Rmd thanks to `pkgload::load_all()` to make it available
and `system.file()` to read it in your examples.
-->

```{r development-2}
# Run all this chunk in the console directly
# Create "inst/" directory
dir.create(here::here("data"))

# Example dataset

# Make your dataset file available to the current Rmd
pkgload::load_all(path = here::here(), export_all = FALSE)


```


# The first function of the package: Calculate the median of a vector

<!--
Create a chunk for the core of the function

- The chunk needs to be named `function` at least
- It contains the code of a documented function
- The chunk can also be named `function-my_median` to make it easily
findable in your Rmd
- Let the `@examples` part empty, and use the next `examples` chunk instead

After inflating the template

-  This function code will be added in a new file in the "R/" directory
-->

```{r function-bmi}
#' BMI
#'
#' @param mass Enter the weight in kg
#' @param height Enter the height in meters
#' @return Returns the body mass index (BMI)
#' 
#' @export
#'
#' @examples
bmi <- function(mass, height){
  mass <- as.numeric(mass)
  height <- as.numeric(height)
  bmi_calculated <- mass/(height * height)
  return(round(bmi_calculated, digits = 1))
}
```

<!--
Create a chunk with an example of use for your function

- The chunk needs to be named `examples` at least
- It contains working examples of your function
- The chunk is better be named `examples-my_median` to be handled
correctly when inflated as a vignette

After inflating the template

-  This example will be added in the '@examples' part of our function above in the "R/" directory
- This example will be added in the vignette created from this Rmd template
-->

```{r examples-bmi}
library(dplyr)

bmi(mass = 80, height = 1.80) # Should give 24.7

#To insert BMI column on a data frame
data("data_weight")
data_weight %>%
  mutate(bmi = bmi(mass = mass, height = height))
```

<!--
Create a chunk with a test of use for your function

- The chunk needs to be named `tests` at least
- It contains working tests of your function
- The chunk is better be named `tests-my_median` to be handled
correctly when inflated as a vignette

After inflating the template

-  This test code will be added in the "tests/testthat/" directory
-->

```{r tests}
library(testthat)
test_that("The bmi function calculates the BMI correctly with the given example", {
  test_bmi <- bmi(mass = 80, height = 1.80)
  expect_equal(test_bmi, 24.7)
})
```



<!--
There can be other functions, examples and tests in your flat template.
Each of them will be inflated in a different file, provided that there is a level-1 or level-2 section title to separate from previous functions.
-->



<!--
# There can be development actions

Create a chunk with 'development' actions

- The chunk needs to be named `development` or `dev`
- It contains functions that are used for package development only
- Note that you may want to store most of these functions in the 0-dev_history.Rmd file

These are only included in the present flat template file, their content will not be part of the package anywhere else.
-->

```{r development-inflate, eval=FALSE}
# Keep eval=FALSE to avoid infinite loop in case you hit the knit button
# Execute in the console directly
fusen::inflate(flat_file = "dev/flat_full.Rmd", vignette_name = "Get started", overwrite = TRUE)
```


# Inflate your package

You're one inflate from paper to box.
Build your package from this very Rmd using `fusen::inflate()`

- Verify your `"DESCRIPTION"` file has been updated
- Verify your function is in `"R/"` directory
- Verify your test is in `"tests/testthat/"` directory
- Verify this Rmd appears in `"vignettes/"` directory
